Using pressure-driven flow systems to evaluate laser speckle contrast imaging

### 2022-06-22 article.tex
Add discussion. Revise conclusion. More edits.

Monitoring cerebral blood flow (CBF) is essential during neurosurgery as it provides surgeons with the critical information needed to guide life-saving interventions and is a valuable tool in mitigating post-operative complications \cite{Kirkness.2005}. As such, a clinical system that provides continuous CBF monitoring is highly desired. Laser speckle contrast imaging (LSCI) is a noninvasive, label-free, optical imaging technique based on coherent dynamic light scattering that has been widely implemented for visualizing changes in blood flow \cite{Briers:2001hy,Boas:2010vr}. Requiring only a laser for illumination and a camera for detection, LSCI can produce full-field maps of motion with high spatiotemporal resolution. This has produced great interest in using LSCI for imaging flow in preclinical neuroscience research \cite{Dunn:2001dj,Ayata:2004ba,Bolay:2002jg,Durduran.2004} as well as a broad set of clinical applications spanning the skin \cite{Briers:1996kfa,Choi:2004jn}, retina \cite{Briers.1982,Srienc.2010}, and neurosurgical use \cite{Hecht:2009gu,Parthasarathy:2010gh,Klijn:2012ls}.

Due to its wide adoption, LSCI instrument design and development is an active area of research, and microfluidic studies are commonly used to quantify controlled flow changes in well-defined channels. Typically, studies designed to mimic blood flow involve the use of a flow channel embedded in a polydimethylsiloxane (PDMS) background \cite{Parthasarathy:2008el}, glass capillary tubing \cite{Choi:2004jn}, or clear plastic tubing \cite{Miao:2014}. More complex microfluidic networks have also been fabricated in glass, plastic, and epoxy substrates to represent superficial heterogenous vasculature \cite{Luu.2012}. A scattering solution \cite{Parthasarathy:2008el} or whole blood\cite{Choi:2004jn,Miao:2014} is then flowed through the channel at controlled rates and imaged. For applications in rodent studies, 0.1 -- 10 mm/s is a commonly selected range of speeds, since this corresponds to the capillary speeds measured in rodents \cite{Tomita:2008do}. This speed is converted to a flow rate using the cross-sectional area of the flow channel, which is used to program the flow control system.

Syringe pumps are the most widely used flow control system in microfluidic studies and are commonly believed to provide a highly-controlled flow output. \textcolor{red}{A review on the subject in 2016 \cite{Richards.2015} found that in the LSCI community, all published microfluidic studies ($>$20) used syringe pumps}; this trend has continued to this date with more recent papers continuing to use syringe pump systems for flow control \cite{Zheng:2018ct,Yang.2019}. However, syringe pumps produce oscillations in flow with varying frequency and magnitude due to the physical motion of the motor and from imperfections on the lead screw \cite{Korczyk:2010eu,Li:2014ca}. Syringe pumps have also been shown to have slow responsivity and take a longer time to achieve desired flow rates \cite{Zhou:2011ey}. The trade-off between stability and responsivity makes it difficult to obtain both stable flow and fast flow response with a syringe pump flow control system.

A pressure-driven flow regulation system can overcome the limitations of a syringe pump by eliminating the use of a motor altogether and can provide very stable flow rates \cite{Korczyk:2010eu,Li:2014ca,Zhou:2011ey}. This method involves using compressed air and a pressure regulator to pressurize a reservoir holding the solution, and then applying a controlled pressure to push solution through the microfluidic device at constant flow rates. A feedback loop, with an in-line flow measurement device, can be used to adjust the pressure level to achieve a desired flow rate, which allows the user to request a desired flow rate rather than a pressure level.

One of the primary limitations of LSCI is the difficulty to accurately provide a quantitative assessment of flow, as demonstrated by its weak correlation with \textit{in vivo} absolute flow velocities in animal studies \cite{Kazmi:2013hp}. Standard LSCI systems use a single camera exposure time, limiting flow sensitivity to a small range. Additionally, several instrumentation factors, namely, illumination variations and noise across different imaging sessions, limits LSCI to intra-patient usage at a single time point and prevents LSCI from providing the quantitative flow data that would be necessary to assist in surgical decision-making. An extension to LSCI called multi-exposure speckle imaging (MESI) has been developed that improves upon many of the shortcomings of LSCI, especially the quantitative accuracy \cite{Parthasarathy:2008el}. MESI has been shown to be reliable for chronic imaging and to have high correlation with \textit{in vivo} absolute velocities in animal studies \cite{Kazmi:2013hp}, suggesting potential for accurate intra- and inter-patient comparisons. By using multiple camera exposure times spanning multiple decades and a more robust mathematical model to estimate flow velocity, the MESI technique has higher accuracy and sensitivity compared to LSCI \cite{Parthasarathy:2008el}.

@@

\subsection{Microfluidic Phantom Fabrication}
\label{sect:methods_phantom}
The microfluidic flow phantom was cast using PDMS (Sylgard 184™, Dow Corning) with 1.8 mg titanium dioxide (\ce{TiO2}) per gram of PDMS added to generate a scattering background that mimicked tissue optical properties ($\mu_s' = 8$ cm$^{-1}$) \cite{Parthasarathy:2008el,Yaroslavsky:2002tg}. The PDMS \ce{TiO2} mixture was vigorously mixed for 15 minutes to ensure even distribution of the \ce{TiO2} in the phantom. Centrifugation (3000 g relative centrifugal force, 10 minutes) was then performed to de-gas the sample and remove any \ce{TiO2} clumps.

A machined aluminum mold was used to cast the microfluidic as shown in Fig.~\ref{fig:microfluidic}a. The extrusion is 460 $\mu$m $\times$ 460 $\mu$m $\times$ 25 mm, which formed three walls of the channel. The square cross-section (1:1 aspect ratio) roughly matches the circular cross-section of vascular geometries \textit{in vivo}. The PDMS \ce{TiO2} mixture was carefully poured on top of the mold within a polystyrene petri dish and placed in a vacuum chamber to remove air bubbles introduced during pouring. The PDMS was then cured at 70 $^\circ$C for 45 -- 60 minutes, allowed to cool, and detached from the mold. The microchannel side of the phantom was oxygen plasma bonded to a glass slide to seal the channel. Inlet and outlet ports were attached using 23G blunt tip needles fitted partially inside the phantom, which were epoxied in place for an air-tight seal. Tygon® microbore tubing (0.02$''$ inner diameter, Cole Parmer Instrument Company, LLC.) was used to connect to the blunt tip ports as inlet and outlet tubing. The inlet tubing was connected to the flow sensor and the flow control system using fluidic fittings with FEP tubing (IDEX Health and Science, LLC.). The outlet tubing drained into a vial, with the tubing end submerged in solution. A photograph of the finished phantom is shown in Fig.~\ref{fig:microfluidic}b, where the channel is visible inside the white PDMS and the glass slide seals the surface.

% Figure 1 - Microfluidic Flow Phantom
\begin{figure}
    \includegraphics[width=\textwidth]{Figure1.pdf}
    \caption {
        (a) Photograph of the machined aluminum mold with a 460 $\mu$m $\times$ 460 $\mu$m $\times$ 25 mm, extrusion used to cast the PDMS during fabrication of the microfluidic flow phantom. (b) Photograph of the finished microfluidic flow phantom, showing PDMS bonded to a glass slide, with inlet and outlet ports secured using epoxy. Tubing was secured to the ports and connected with the rest of the system using fluidic fittings.
    }
    \label{fig:microfluidic}
\end{figure}

A colloidal mixture of suspended 1 $\mu$m diameter polystyrene microspheres (10\% w/w, 5100A, Thermo Fisher Scientific, Inc.) in ultra-filtered de-ionized (UFDI) water was used as a blood-mimicking solution. Based on Ref. \cite[]{Roggan:1999bz}, the reduced scattering coefficient ($\mu_s'$) of whole blood with hematocrit = 0.5 is approximately 20 cm$^{-1}$. By using a 7\% by volume mixture of the polystyrene microsphere solution and UFDI water (for example, a 10 mL batch of the blood mimicking solution would be made up of by 0.7 mL of the 5100A solution and 9.3 mL UFDI water) we are able to achieve a calculated $\mu_s'$ of 19.8 cm$^{-1}$. However, we note that the anisotropy of the microspheres in our solution is different that that of whole blood ($g = 0.92$ compared to $g = 0.98$). The blood-mimicking solution was preferred over whole blood for several reasons, namely: cleaning and safety, ease of acquisition, and because the flow sensor was factory-calibrated for deionized water flow. Since the concentration of microspheres was very low (0.7\% by weight in the final suspension), the water calibration of the flow sensor remained valid. The solution of microspheres was freshly mixed before each experiment to reduce aggregation of particles in the dilution. Once mixed, the solution was sonicated (10 minutes) to fully suspend the particles and then de-gassed under vacuum to eliminate air bubbles.

@@

To assess the performance of the syringe pump and pressure-regulated flow systems, and to quantify the uncertainty of each system, it is necessary to know the true flow rate of the blood-mimicking solution through the microfluidic channel. A mass flow sensor (FLU-L, 0 -- 1 mL/min, Fluigent, Inc.) was placed inline between the flow control system and the phantom inlet tubing, as shown in Fig.~\ref{fig:system_lsci}a. The sensor was connected to a flow reader (Flow Board, FLB, Fluigent, Inc.) to digitize the sensor output and the MAESFLO software (Fluigent, Inc.) was used to record the absolute flow rate. All flow sensor measurements were downsampled from 10 Hz to 2 Hz using interpolation to match the timing of the optical measurements.

The syringe pump system (74905-04, Cole-Parmer Instrument Company, LLC.) was connected to the flow sensor, as shown in Fig.~\ref{fig:system_lsci}b, and a 10 mL plastic syringe (BD \#302149) was filled with blood-mimicking solution as described in Section \ref{sect:methods_phantom}. The syringe pump was programmed to run the desired flow profile, using the inner diameter of the syringe to ensure correct flow rate output. It should be noted that a 3 mL syringe was also tested, however its performance was significantly worse than the 10 mL syringe and, in some cases, could not resolve the desired flow profiles.

The pressure-regulated flow system used a pressure controller base unit (MFCS-EZ with 69 mbar channel, Fluigent, Inc.), powered by a house air line regulated to maintain 500 mbar of pressure, as shown in Fig.~\ref{fig:system_lsci}c. This controller outputted regulated air flow (up to 69 mbar) to a 15 mL pressurized reservoir (Fluiwell-1C, Fluigent, Inc.) filled with the blood-mimicking solution. Prior to running a flow program, a calibration was performed that accounted for the resistance from the tubing, microfluidic channel, and hydrostatic pressure. The pressure control system used built-in software (MAESFLO) to provide feedback from the inline flow sensor to regulate the pressure to achieve the desired flow rate.

@@

Finally, the uncertainty in measurement bias, was defined as:
%
% Equation 3 - Uncertainty in Bias
\begin{equation}
    \label{eq:u_bias}
    u_\textnormal{bias} = 100 \left| \frac{\bar{x} - x_{ref}}{x_{ref}} \right|
\end{equation}

@@

A schematic of the LSCI setup is shown in Fig.~\ref{fig:system_lsci}a. Measurements were performed using a 660 nm laser diode (HL6545MG, Thorlabs Inc.) mounted in a temperature-controlled housing (LDM21, Thorlabs Inc.) and expanded using an aspheric lens to obliquely illuminate the microfluidic. The laser diode controller (LDC205C, Thorlabs, Inc.) was set to 200 mA ($\sim$120 mW) while the temperature controller (TED200C, Thorlabs Inc.) was set to 10.5 k$\Omega$ (23.8 $^\circ$C). A pair of fixed focal length consumer camera lenses (AF Nikkor 50 mm $f$/1.8D, Nikon Corp.) were placed in tandem with infinity focus for 1:1 imaging. \textcolor{red}{Is there a filter? Specifics of f-number and speckle size?} The scattered light was imaged with a CCD camera (piA640-210gm, 648 $\times$ 488 pixels, Basler AG) controlled using custom software written in C++. The full sensor array was used, resulting in a field-of-view of 4.8 $\times$ 3.6 mm. The camera exposure time was set to 0.5 ms and allowed to run at full speed, resulting in an effective acquisition rate of $\sim$150 frames-per-second (fps). \textcolor{red}{Explanation for 0.5 ms exposure time?}

@@

To validate the flow sensor measurements, single-exposure LSCI was used to simultaneously image the microfluidic flow phantom during the 13-step flow experiments described in Section \ref{sect:methods_flow_assess}. Raw intensity images were converted to speckle contrast images using Eq. \ref{eq:sc}, where speckle contrast ($K$) is defined as the ratio of the standard deviation ($\sigma_{s}$) to the mean intensity ($\langle{I}\rangle$) in a sliding 7$\times$7-pixel window centered at every pixel.
%
% Equation 4 - Speckle Contrast
\begin{equation}
    \label{eq:sc}
    K = \frac{\sigma_{s}}{\langle{I}\rangle}
\end{equation}

By incorporating efficient processing techniques\cite{Tom:2008tg} into the acquisition software, speckle contrast images were computed, displayed, and saved in real-time. \textcolor{red}{Unclear if there was additional averaging performed by the Speckle Software (i.e. frames/sequence=15? Was the saved SC data already averaged?)} During post-processing, the average speckle contrast was extracted from each frame within a region centered in the microfluidic channel. This value was used to estimate the correlation time ($\tau_{c}$) of the speckle autocorrelation function, which is considered a more quantitative measure of flow \cite{Briers:1996kfa}. The averaged speckle contrast value at each timepoint was fitted for its corresponding $\tau_{c}$ using Eq. \ref{eq:lsci},
%
% Equation 5 - LSCI Equation
\begin{equation}
    \label{eq:lsci}
    K^2(T, \tau_{c}) = \beta\frac{e^{-2x}-1+2x}{2x^2}
\end{equation}

@@

Because $\tau_c$ is inversely related to the speed of moving scatterers in the sample \cite{Bonner:1981hg}, the inverse correlation time ($ICT = 1/\tau_c$) is commonly used for visualization. In order to compare the LSCI measurements with the flow sensor, the relative flow for each technique was calculated using the average value of the first step (2.4 mm/s) as the baseline. The initial rise of the first flow step was also used to synchronize the timing of the two datasets.

@@

A schematic of the MESI setup is shown in Fig.~\ref{fig:system_mesi}. MESI was performed \cite{Parthasarathy:2008el} using a wavelength-stabilized 785 nm laser diode (LD785-SEV300, Thorlabs, Inc.) mounted in a temperature-controlled housing (TCLDM9, Thorlabs, Inc.) and collimated using an aspheric lens (C280TMD-B, Thorlabs, Inc.). The operating current on the laser diode controller (LDC205C, Thorlabs, Inc.) was fixed at 380 mA (300 mW) and the target temperature set to 25 $^\circ$C on the temperature controller (TED200C, Thorlabs, Inc.). The collimated laser light was passed through a free-space optical isolator (Electro-Optics Technology, Inc.) to minimize back reflections that interfere with single frequency performance. Because the external volume holographic grating of the stabilized laser diode produces a dark spot in the far field, the laser was coupled \textcolor{red}{(Which lens?)} into a single-mode patch cable (P3-780A-FC-2, Thorlabs, Inc.) to obtain a Gaussian beam. The fiber output was re-collimated (F230APC-780, Thorlabs, Inc.), intensity modulated with an acousto-optic modulator (AOM, 3100-125; RF Driver 1110AF-AIFO-1.0, Gooch \& Housego, Ltd.), and relayed to obliquely illuminate the microfluidic.

A pair of consumer camera lenses were used to image the scattered light (AF Nikkor 50 mm $f$/1.8D + AF Micro-Nikkor 105 mm $f$/2.8D, Nikon Corp.) with 2.1$\times$ magnification through a bandpass filter (785$\pm$31 nm, 87-773, Edmund Optics Inc.) to a CMOS camera (acA1920-155um, 1920 $\times$ 1200 pixels, Basler AG). Only a subset of the overall sensor array was used (1000 $\times$ 750 pixels), resulting in a field-of-view of 2.9 $\times$ 2.2 mm. The camera exposures were temporally synchronized with the modulated laser pulses. Fifteen different camera exposures ranging between 50 $\mu$s and 80 ms were recorded for each complete MESI frame, resulting in an effective acquisition rate of approximately 2.5 fps. The total amount of light used to capture each exposure was held constant with the AOM in order to minimize the effects of shot noise \cite{Parthasarathy:2008el}. The entire acquisition was controlled using custom software written in C++ along with a multifunction I/O device (USB-6363, National Instruments Corp.) for the generation of camera exposure trigger signals and AOM modulation voltages.

% Figure 3 - MESI System Schematic
\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Figure3.pdf}
    \caption {
        System schematic for microfluidic flow assessment of MESI and LSCI with the pressure-regulated flow system.
    }
    \label{fig:system_mesi}
\end{figure}

@@

A stepped flow profile experiment was conducted using the pressure-regulated flow system to assess the performance of both MESI and LSCI. The flow profile consisted of 19 steps spanning 1 -- 10 mm/s in 0.5 mm/s increments. Each speed was maintained for two minutes with a total duration of 40 minutes, including brief periods of no flow (0 mm/s) at the beginning and end of the profile. MESI measurements were acquired continuously throughout the experiment at the maximum acquisition rate of the system ($\sim$2.5 fps). Single-exposure (0.5 ms) LSCI measurements were extracted from the MESI dataset \textit{post hoc}. Because the flow sensor software used a separate clock than the MESI acquisition, the datasets were synchronized during post-processing using the initial rise of the first flow step. The experiment was repeated a total of four times across two days.

The raw intensity images were converted to speckle contrast images and the average value within the microfluidic channel extracted from each frame as described in Section \ref{sect:methods_lsci}. The average speckle contrast values from all fifteen exposure times were then fitted to the multi-exposure speckle visibility equation \cite{Parthasarathy:2008el} to obtain an estimate of $\tau_c$,
%
% Equation 6 - MESI Equation
\begin{equation}
    \label{eq:mesi}
    K^2(T,\tau_c) =
        \beta\rho^2\frac{e^{-2x} - 1 + 2x}{2x^2} +
        4\beta\rho(1 - \rho)\frac{e^{-x} - 1 + x}{x^2} +
        \nu
\end{equation}

>>>>

Monitoring cerebral blood flow (CBF) is essential during neurosurgery as it provides surgeons with the critical information needed to guide life-saving interventions and is a valuable tool in mitigating post-operative complications \cite{Kirkness.2005}. As such, a clinical system that provides continuous CBF monitoring is highly desired. Laser speckle contrast imaging (LSCI) is a noninvasive, label-free, optical imaging technique based on coherent dynamic light scattering that has been widely implemented for visualizing changes in blood flow \cite{Briers:2001hy,Boas:2010vr}. Requiring only a laser for illumination and a camera for detection, LSCI can produce full-field maps of motion with high spatiotemporal resolution. This has produced great interest in using LSCI for imaging flow in preclinical neuroscience research \cite{Dunn:2001dj,Ayata:2004ba,Bolay:2002jg,Durduran.2004} as well as a broad set of clinical applications spanning the skin \cite{Briers:1996kfa,Choi:2004jn}, retina \cite{Briers.1982,Srienc.2010}, and brain \cite{Hecht:2009gu,Parthasarathy:2010gh,Klijn:2012ls}.

Due to its widespread adoption, LSCI instrument design and development is an active area of research with microfluidic studies commonly used to quantify controlled flow changes in well-defined channels. Typically, studies designed to mimic blood flow involve the use of a flow channel embedded in a polydimethylsiloxane (PDMS) background \cite{Parthasarathy:2008el}, glass capillary tubing \cite{Choi:2004jn}, or clear plastic tubing \cite{Miao:2014}. More complex microfluidic networks have also been fabricated in glass, plastic, and epoxy substrates to represent superficial heterogenous vasculature \cite{Luu.2012}. A scattering solution \cite{Parthasarathy:2008el} or whole blood\cite{Choi:2004jn,Miao:2014} is then flowed through the channel at controlled rates and imaged using LSCI. For applications in rodent studies, 0.1 -- 10 mm/s is a commonly selected range of flow speeds that corresponds with experimentally measured capillary speeds \cite{Tomita:2008do}. This speed can be converted to a flow rate using the cross-sectional area of the flow channel, which is used to program the flow control system.

Syringe pumps are the most widely used flow control system in microfluidic studies and are believed to provide a highly-controlled flow output. A survey of 21 LSCI studies using microfluidics that were published since 2015 found that syringe pumps were used in the majority (90\%) of experiments. The devices were from a variety of manufacturers and featured various syringe sizes and materials. However, syringe pumps produce oscillations in flow with varying frequency and magnitude due to the physical motion of the motor and from imperfections on the lead screw \cite{Korczyk:2010eu,Li:2014ca}. Syringe pumps have also been shown to have slow responsivity and take a longer time to achieve desired flow rates \cite{Zhou:2011ey}. The trade-off between stability and responsivity makes it difficult to obtain both stable flow and fast flow response with a syringe pump flow control system.

A pressure-driven flow regulation system can overcome the limitations of a syringe pump by eliminating the use of a motor and lead screw in order to provide very stable flow \cite{Korczyk:2010eu,Li:2014ca,Zhou:2011ey}. These systems use compressed air to push liquid from a pressure-regulated reservoir through the microfluidic device at constant flow rates. Integration with an inline flow measurement device allows for feedback loop control and the programming of specific flow rates rather than pressure levels.

One of the primary limitations of LSCI is the difficulty to accurately provide a quantitative assessment of flow, as demonstrated by its weak correlation with \textit{in vivo} absolute flow velocities in animal studies \cite{Kazmi:2013hp}. Standard LSCI systems use a single camera exposure time, limiting sensitivity to a small range of flows. Additionally, instrumentation factors such as illumination variation and noise across different imaging sessions, limits LSCI to intra-patient usage at a single time point and prevents LSCI from providing the quantitative flow data that would be necessary to assist in surgical decision-making. An extension to LSCI called multi-exposure speckle imaging (MESI) has been developed that improves upon many of the shortcomings of LSCI, especially the quantitative accuracy \cite{Parthasarathy:2008el}. MESI has been shown to be reliable for chronic imaging and to have high correlation with \textit{in vivo} absolute velocities in animal studies \cite{Kazmi:2013hp}, suggesting potential for accurate intra- and inter-patient comparisons. By using multiple camera exposure times spanning multiple decades and a more robust mathematical model to estimate flow velocity, the MESI technique has higher accuracy and sensitivity compared to LSCI \cite{Parthasarathy:2008el}.

@@

\subsection{Microfluidic Phantom Fabrication}
\label{sect:methods_phantom}
The microfluidic flow phantom was cast using PDMS (Sylgard 184™, Dow Corning) with 1.8 mg titanium dioxide (\ce{TiO2}) added per gram of PDMS to generate a scattering background that mimicked tissue optical properties ($\mu_s' = 8$ cm$^{-1}$) \cite{Parthasarathy:2008el,Yaroslavsky:2002tg}. The PDMS \ce{TiO2} mixture was vigorously mixed for 15 minutes to ensure even distribution of the \ce{TiO2} in the phantom. Centrifugation (3000 g relative centrifugal force, 10 minutes) was then performed to de-gas the sample and remove any \ce{TiO2} clumps.

A machined aluminum mold was used to cast the microfluidic as shown in Fig.~\ref{fig:microfluidic}a. The extrusion is 460 $\mu$m $\times$ 460 $\mu$m $\times$ 25 mm, which formed three walls of the channel. The square cross-section (1:1 aspect ratio) roughly matches the circular cross-section of vascular geometries \textit{in vivo}. The PDMS \ce{TiO2} mixture was carefully poured on top of the mold within a polystyrene petri dish and placed in a vacuum chamber to remove air bubbles introduced during pouring. The PDMS was then cured at 70 $^\circ$C for 45 -- 60 minutes, allowed to cool, and detached from the mold. The microchannel side of the phantom was oxygen plasma bonded to a glass slide to seal the channel. Inlet and outlet ports were attached using 23 G blunt tip needles fitted partially inside the phantom, which were epoxied in place for an air-tight seal. Tygon® microbore tubing (0.02$''$ inner diameter, Cole Parmer Instrument Company, LLC.) was connected to the blunt tip ports as inlet and outlet tubing. The inlet tubing was connected to the flow control system using fluidic fittings with FEP tubing (IDEX Health and Science, LLC.). The outlet tubing drained into a vial, with the tubing end fully submerged in liquid. A photograph of the phantom is shown in Fig.~\ref{fig:microfluidic}b, where the channel is visible inside the white PDMS with the glass slide sealing the surface.

% Figure 1 - Microfluidic Flow Phantom
\begin{figure}
    \includegraphics[width=\textwidth]{Figure1.pdf}
    \caption {
        (a) Photograph of the machined aluminum mold with a 460 $\mu$m $\times$ 460 $\mu$m $\times$ 25 mm extrusion used to cast the PDMS during fabrication of the microfluidic flow phantom. (b) Photograph of the finished microfluidic flow phantom, showing PDMS bonded to a glass slide, with inlet and outlet ports secured using epoxy. Tubing was secured to the ports and connected with the rest of the system using fluidic fittings.
    }
    \label{fig:microfluidic}
\end{figure}

A colloidal mixture of suspended 1 $\mu$m diameter polystyrene microspheres (10\% w/w, 5100A, Thermo Fisher Scientific, Inc.) in ultra-filtered de-ionized (UFDI) water was used as a blood-mimicking solution. Based on Ref. \cite[]{Roggan:1999bz}, the reduced scattering coefficient ($\mu_s'$) of whole blood with hematocrit of 0.5 is approximately 20 cm$^{-1}$. By using a 7\% by volume mixture of the polystyrene microsphere solution and UFDI water (for example, a 10 mL batch of the blood mimicking solution would be made up of 0.7 mL of the 5100A solution and 9.3 mL UFDI water) we are able to achieve a calculated $\mu_s'$ of 19.8 cm$^{-1}$. However, we note that the anisotropy of the microspheres in our solution is different than that of whole blood ($g = 0.92$ versus $g = 0.98$). The blood-mimicking solution was preferred over whole blood for several reasons: cleaning and safety, ease of acquisition, and because the flow sensor was factory-calibrated for deionized water. Since the concentration of microspheres was very low (0.7\% by weight in the final suspension), the water calibration of the flow sensor remained valid. The solution of microspheres was freshly mixed before each experiment to reduce aggregation of particles in the dilution. Once mixed, the solution was sonicated for 10 minutes to fully suspend the particles and then de-gassed under vacuum to eliminate air bubbles.

@@

To assess the performance of the syringe pump and pressure-regulated flow systems, and to quantify the uncertainty of each system, it is necessary to know the true flow rate of the blood-mimicking solution through the microfluidic channel. A thermal mass flow sensor (FLU-L, 0.03 -- 1 mL/min, Fluigent, Inc.) was placed inline between the flow control system and the phantom inlet tubing, as shown in Fig.~\ref{fig:system_lsci}a. The sensor output was digitized and relayed to a computer via an accompanying hub (Flowboard, FLB, Fluigent, Inc.) where the MAESFLO software (Fluigent, Inc.) was used to monitor and record the absolute flow rate. All flow sensor measurements were downsampled from 10 Hz to 2 Hz using interpolation to match the timing of the optical measurements.

The syringe pump system (EW-74905-04, Cole Parmer Instrument Company, LLC.) was connected to the flow sensor (Fig.~\ref{fig:system_lsci}b) and a 10 mL plastic syringe (\#302149, BD) was filled with the blood-mimicking solution described in Section \ref{sect:methods_phantom}. The syringe pump was programmed to run a predefined flow profile, using the inner diameter of the syringe (14.5 mm) to ensure correct flow rate output. It should be noted that a 3 mL syringe was also evaluated, however its performance was significantly worse than the 10 mL syringe and regularly failed to resolve the desired flow profiles.

The pressure-regulated flow system used a pressure controller (MFCS-EZ with 69 mbar channel, Fluigent, Inc.) connected to a house air line regulated at 500 mbar, as shown in Fig.~\ref{fig:system_lsci}c. This controller outputted regulated air flow (up to 69 mbar) to a 15 mL pressurized reservoir (Fluiwell-1C, Fluigent, Inc.) filled with the blood-mimicking solution. Prior to running a flow program, a calibration was performed that accounted for the resistance from the tubing, microfluidic channel, and hydrostatic pressure. The MAESFLO control software used feedback from the inline flow sensor to regulate the air pressure to achieve the desired flow rate.

@@

Finally, the uncertainty in measurement bias, an estimate of flow accuracy, was defined as:
%
% Equation 3 - Uncertainty in Bias
\begin{equation}
    \label{eq:u_bias}
    u_\textnormal{bias} = 100 \left| \frac{\bar{x} - x_{ref}}{x_{ref}} \right|
\end{equation}

@@

A schematic of the LSCI setup is shown in Fig.~\ref{fig:system_lsci}a. Measurements were performed using a 660 nm laser diode (HL6545MG, Thorlabs Inc.) mounted in a temperature-controlled housing (LDM21, Thorlabs Inc.) and expanded using an aspheric lens to obliquely illuminate the microfluidic. The laser diode controller (LDC205C, Thorlabs, Inc.) was set to 200 mA ($\sim$120 mW) while the temperature controller (TED200C, Thorlabs Inc.) was set to 10.5 k$\Omega$ (23.8 $^\circ$C). A pair of fixed focal length consumer camera lenses (AF Nikkor 50 mm $f$/1.8D, Nikon Corp.) were placed in tandem with infinity focus for 1:1 imaging. The aperture of the lower lens was set to 
$f$/11 in order to properly sample the speckle pattern \cite{Kirkpatrick:2008ke} while the upper lens was left at its maximum size of $f$/1.8. A longpass red filter (600 nm, R-60, Edmund Optics, Inc.) was placed between the two lenses to filter stray background light. The scattered light was imaged with a CCD camera (piA640-210gm, 648 $\times$ 488 pixels, Basler AG) controlled using custom software written in C++. The full sensor array was used, resulting in a field-of-view of 4.8 $\times$ 3.6 mm. The camera exposure time was set to 0.5 ms 
and allowed to run at full speed, resulting in an effective acquisition rate of $\sim$150 frames-per-second (fps).

@@

To validate the flow sensor measurements, single-exposure LSCI was used to simultaneously image the microfluidic flow phantom during the 13-step flow experiments described in Section \ref{sect:methods_flow_assess}. Raw intensity images were converted to speckle contrast images using Eq. \ref{eq:sc}, where speckle contrast ($K$) is defined as the ratio of the standard deviation ($\sigma_{s}$) to the mean intensity ($\langle{I}\rangle$) in a sliding 7$\times$7-pixel window centered at every pixel of the raw image.
%
% Equation 4 - Speckle Contrast
\begin{equation}
    \label{eq:sc}
    K = \frac{\sigma_{s}}{\langle{I}\rangle}
\end{equation}

By incorporating efficient processing techniques\cite{Tom:2008tg} into the acquisition software, speckle contrast images were computed, displayed, and saved in real-time. During post-processing, the average speckle contrast was extracted from each frame within a region centered in the microfluidic channel. This value was used to estimate the correlation time ($\tau_{c}$) of the speckle autocorrelation function, which is considered a more quantitative measure of flow \cite{Briers:1996kfa}. The averaged speckle contrast value at each timepoint was fitted for its corresponding $\tau_{c}$ using Eq. \ref{eq:lsci},
%
% Equation 5 - LSCI Equation
\begin{equation}
    \label{eq:lsci}
    K^2(T, \tau_{c}) = \beta\frac{e^{-2x}-1+2x}{2x^2}
\end{equation}

@@

Because $\tau_c$ is inversely related to the speed of moving scatterers in the sample \cite{Bonner:1981hg}, the inverse correlation time ($ICT = 1/\tau_c$) is commonly used for visualization. In order to compare the LSCI measurements with the flow sensor, the relative flow for each technique was calculated using the average value of the first step (2.4 mm/s) as the baseline. Because the flow sensor software used a separate clock than the LSCI acquisition, the datasets were synchronized during post-processing using the initial rise of the first flow step.

@@

A schematic of the MESI setup is shown in Fig.~\ref{fig:system_mesi}. MESI was performed using a wavelength-stabilized 785 nm laser diode (LD785-SEV300, Thorlabs, Inc.) mounted in a temperature-controlled housing (TCLDM9, Thorlabs, Inc.) and collimated using an aspheric lens (C280TMD-B, Thorlabs, Inc.). The operating current on the laser diode controller (LDC205C, Thorlabs, Inc.) was fixed at 380 mA (300 mW) and the target temperature set to 25 $^\circ$C on the temperature controller (TED200C, Thorlabs, Inc.). The collimated laser light was passed through a free-space optical isolator (Electro-Optics Technology, Inc.) to minimize back reflections that interfere with single frequency performance. Because the external volume holographic grating of the stabilized laser diode produces a dark spot in the far field, the laser was coupled into a single-mode fiber optic patch cable (P3-780A-FC-2, Thorlabs, Inc.) to obtain a Gaussian beam. The fiber output was re-collimated (F230APC-780, Thorlabs, Inc.), intensity modulated with an acousto-optic modulator (AOM, 3100-125; RF Driver 1110AF-AIFO-1.0, Gooch \& Housego, Ltd.), and relayed to obliquely illuminate the microfluidic.

A pair of consumer camera lenses were used to image the scattered light (AF Nikkor 50 mm $f$/1.8D + AF Micro-Nikkor 105 mm $f$/2.8D, Nikon Corp.) with 2.1$\times$ magnification through a bandpass filter (785$\pm$31 nm, 87-773, Edmund Optics Inc.) to a CMOS camera (acA1920-155um, 1920 $\times$ 1200 pixels, Basler AG). The aperture of the lower lens was set to $f$/5.6 while the upper lens was left at its maximum size of $f$/2.8. Only a subset of the overall sensor array was used (1000 $\times$ 750 pixels), resulting in a field-of-view of 2.9 $\times$ 2.2 mm. The camera exposures were temporally synchronized with the modulated laser pulses. Fifteen different camera exposures ranging between 50 $\mu$s and 80 ms were recorded for each complete MESI frame, resulting in an effective acquisition rate of approximately 2.5 fps. The total amount of light used to capture each exposure was held constant with the AOM in order to minimize the effects of shot noise \cite{Parthasarathy:2008el}. The entire acquisition was controlled using custom software written in C++ integrated with a multifunction I/O device (USB-6363, National Instruments Corp.) for the generation of camera exposure trigger signals and AOM modulation voltages.

% Figure 3 - MESI System Schematic
\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Figure3.pdf}
    \caption {
        System schematic for microfluidic flow assessment of MESI and LSCI measurements using only the pressure-regulated flow system.
    }
    \label{fig:system_mesi}
\end{figure}

@@

A stepped flow profile experiment was conducted using the pressure-regulated flow system to assess the performance of both MESI and LSCI. The flow profile consisted of 19 steps spanning 1 -- 10 mm/s in 0.5 mm/s increments. Each speed was maintained for two minutes with a total duration of 40 minutes, including brief periods of no flow (0 mm/s) at the beginning and end of the profile. MESI measurements were acquired continuously throughout the experiment at the maximum acquisition rate of the system ($\sim$2.5 fps). Single-exposure (0.5 ms) LSCI measurements were extracted from the MESI dataset \textit{post hoc}. The initial rise of the first flow step was again used to synchronize the timing of the MESI/LSCI and flow sensor datasets. The experiment was repeated a total of four times across two days.

The raw intensity images were converted to speckle contrast images and the average value within the microfluidic channel extracted from each frame as described previously in Section \ref{sect:methods_lsci}. The average speckle contrast values from all fifteen exposure times were then fitted to the multi-exposure speckle visibility equation \cite{Parthasarathy:2008el} to obtain an estimate of $\tau_c$,
%
% Equation 6 - MESI Equation
\begin{equation}
    \label{eq:mesi}
    K^2(T,\tau_c) =
        \beta\rho^2\frac{e^{-2x} - 1 + 2x}{2x^2} +
        4\beta\rho(1 - \rho)\frac{e^{-x} - 1 + x}{x^2} +
        \nu
\end{equation}
